Who Needs Privacy?

### 2018-11-14 manuscript/manuscript.tex
- manuscript: included parts of original publication

---
title             : "Who Needs Privacy?"
shorttitle        : "Who Needs Privacy?"

author: 
  - name          : "Tobias Dienlin"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "University of Hohenheim, Department of Media Psychology (540F)"
    email         : "tobias.dienlin@uni-hohenheim.de"
  - name          : "Miriam Metzger"
    affiliation   : "1,2"

affiliation:
  - id            : "1"
    institution   : "University of Hohenheim"
  - id            : "2"
    institution   : "University of California, Santa Barbara"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

@@

abstract: |
  Objective: This study analyzes how personality relates to peoples' desire for privacy. Specifically, we investigated whether the syllogism "I don't mind surveillance because I have nothing to hide" is correct: Do people who lack integrity (given they have something to hide) indeed desire more privacy?

  Method: Study 1 featured an online questionnaire (_N_ = 268, _M_\textsubscript{age} = 20 years, 72\% female) and Study 2 a laboratory experiment (_N_ = 87, _M_\textsubscript{age} = 20 years, 51\% female), where participants wrote an essay about past negative, positive, or neutral behaviors to analyze effects on desire for privacy.

  Results: Study 1 showed that respondents who are more shy, less anxious, and more risk averse desired more privacy. Respondents who self-reported lacking integrity reported desiring more privacy from government and more anonymity. Study 2 replicated these results and showed a statistical trend (_p_ = .052) that writing about negative past behaviors increased desire for interpersonal privacy. Moreover, the integrity IAT showed significant relations with desire for privacy from government.

@@

keywords          : "keywords"
wordcount         : "X"

bibliography      : 
  - "../bibliography/r-references.bib"
  - "../bibliography/references.bib"

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
header-includes:
  - \setlength{\parskip}{0em}
  - \raggedbottom
---

```{r setup, include = FALSE}
library("papaja")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

In his novel _The Circle_, @Eggers.2013 describes a dystopian society in which people are gradually forfeiting their privacy. People decide to become "transparent", which means that they start carrying a small camera around the neck in order to broadcast their daily lives to the Internet. Eventually, this causes a societal upheaval: "The pressure on those who hadn't gone transparent went from polite to oppressive. The question, from pundits and constituents, was obvious and loud: If you aren't transparent, what are you hiding?" [@Eggers.2013, p. 129]. The main argument being offered to justify the surveillance is: "If you have nothing to hide, you have nothing to fear." This syllogism is familiar, given that it commonly appears in also nonfictional conversations [@Sieradski.2013]. Consider, for example, the following tweet: "I don't download illegally. I don't have anything on my comp[uter] to hide. Hell, I'm sure the \#NSA gave up on me years ago." [@BeautifulDisaster.2015].

Why do people desire privacy? To date there is only little research on why people desire privacy and how the desire for privacy can be predicted by aspects of personality. For example, and to the best of our knowledge, so far no study exists that has analyzed the nothing-to-hide argument from a scientific and empirical perspective. Why do some people not care whether government agencies such as the NSA are collecting their data [@Greenwald.2013], and why do others protest vehemently in order to protect their privacy?

@@

## Desire for Privacy

Privacy captures the extent of voluntary withdrawal from others [@Westin.1967]. Several models suggest that privacy is a multi-dimensional concept: For example, in a theory-driven treatise @Burgoon.1982 argued that privacy has four dimensions: informational, social, psychological, and physical privacy. @Pedersen.1979, by contrast, did an empirical factor analysis (initially starting with 94 items) and suggested that privacy exists on six dimensions: reserve, isolation, solitude, intimacy with friends, intimacy with family, and anonymity. In addition, @Schwartz.1968 differentiated between horizontal and vertical privacy: Whereas horizontal privacy captures withdrawal from peers, vertical privacy refers to withdrawal from superiors or institutions (e.g., government agencies). Next to being multi-dimensional, privacy is also contingent [@Dienlin.2014]: One can, for example, distinguish between the objective privacy context, the subsequent subjective perception of privacy, the psychological desire for privacy (which is both a situational and dispositional need), and the resulting privacy behavior (as represented by self-disclosure). For the purpose of this study, we combine the aforementioned theories and focus on (a) vertical privacy with regard to the desire for withdrawal from government surveillance, (b) horizontal privacy in terms of the desire for withdrawal from peers, friends, or acquaintances, and (c) both horizontal and vertical privacy as captured by the general desire for anonymity.

### The relation between integrity and desire for privacy

@@

The NSA surveillance, data mining, or other government information gathering programs will result in the disclosure of particular pieces of information to a few government officials, or perhaps only to government computers. This very limited disclosure of the particular information involved is not likely to be threatening to the privacy of law-abiding citizens. Only those who are engaged in illegal activities have a reason to hide this information. [@Solove.2007; p. 753]

This definition helps illustrate the link between lack of integrity and desire for privacy: People who have "engaged in illegal activities" can be considered, by definition, to lack integrity [@Paunonen.2002], which is why they have a reason "to hide this information" (or, in other words, to desire more privacy). In terms of a scientific definition of integrity there is no real consensus, however most scholars agree that integrity "incorporates a tendency to comply with social norms, avoid deviant behavior, and embrace a sense of justice, truthfulness, and fairness" [@Connelly.2006; p. 82].

Several theoretical arguments exist why lack of integrity might correlate with desire for privacy. In general, any self-disclosure is a potential risk because others might disagree, disapprove, or misuse the information in other contexts [@Petronio.2000]. Privacy regulation theory showed that if self-disclosures are too risky, people raise their desired level of privacy, intensify their boundary regulation, and employ more mechanisms to seclude and protect themselves [@Altman.1976]. In traditional contexts, this could range from moderate behaviors like closing doors, to extreme behaviors such as physically tossing someone out of the room [@Altman.1976]. In modern contexts, protecting one's privacy can mean to avoid photographs or to deliberately shun public places that have surveillance cameras. People who have actually committed something bad, treacherous, or illegal become even more vulnerable and face a significant risk of self-disclosure, because others will surely disapprove of these activities [@Petronio.2000]. Hence, the foregoing arguments illuminate an indirect link between integrity and desire for privacy: By definition, people who participate in negative activities are considered to lack integrity [@Paunonen.2002]. People who have engaged in negative activities have, by definition, more to hide, and disclosures concerning those activities pose a high risk. Because of this increased risk, people will arguably desire more privacy, as a means to mitigate their felt risk [@Altman.1976]. In this way, the current research extends Altman's privacy regulation theory (1976) by suggesting that lack of integrity is an important yet unexamined factor that could increase peoples' desired level of privacy.

A few studies can be found that imply a relation between privacy and integrity. For example, several studies found that surveillance reduces cheating behaviors [@Corcoran.1987, Covey.1989]. @Covey.1989 asked students to solve an impossible maze. In the high surveillance condition, the experimenter stood in front of the students and closely monitored their behavior. In the low surveillance condition, the experimenter stood behind the students, did not monitor their behavior, and visual dividers were used to block the experimenter's view of the students. Results showed that students were more likely to cheat in the low surveillance condition, suggesting that in situations of surveillance (i.e., less privacy), people show fewer cheating behaviors (i.e., more integrity). Similarly, people are more likely to prevent others from stealing when security cameras are visible [@vanBommel.2014], which is also a sign of higher integrity. Next, in a longitudinal sample with 457 respondents in Germany [@Trepte.2013], people who reported needing more privacy were less satisfied with their lives (_r_ = -.47), had more (_r_ = .41) and less positive affect (_r_ = -.39). More importantly however, people who felt they needed more privacy were also less authentic on their SNSs profiles (_r_ = -.48) and less authentic in their personal relationships [_r_ = -.28; @Trepte.2013]. For example, people who agreed to items like "I do not talk about personal issues unless my conversation partner brings them up first" were more likely to report that their online profiles did not truly represent their personality. Given the argument that authenticity is a subset of integrity [@Sheldon.2004], we reason that the concept of integrity might relate to the desired level of privacy. Finally, @Pedersen.1982 showed that three dimensions of need for privacy related to self-esteem: In his study with _N_ = 70 undergraduate students, respondents who held a lower self-esteem were more reserved (_r_ = .29), needed more anonymity (_r_ = .21) and preferred solitude (_r_ = .24). Granted, self-esteem and integrity are generally distinct concepts; however, Pedersen's specific operationalization of self-esteem integrated several aspects of integrity (e.g., by using items such as "moral, nice, fair, unselfish, good, honest, reputable, sane" to measure self-esteem). Thus, our overarching hypothesis is that people who lack integrity have a greater desire for privacy.

@@

### Shyness

Critics of the nothing-to-hide argument hold that people who desire privacy should not automatically be confronted with suspicion, and that privacy has several purposes that are not related to criminal behavior [@Marlinspike.2013]. @Westin.1967, for example, defined four primary purposes of privacy: (1) self-development (i.e., the integration of experiences into meaningful patterns), (2) autonomy (i.e., the desire to avoid being manipulated and dominated), (3) emotional release (i.e., the release of tension from social role demands), and (4) protected communication (i.e., the ability to foster intimate relationships). These are all important social factors for which people desire privacy. Hence, the argument is that people who desire privacy can have several legitimate reasons for doing so; reasons which are essential for psychosocial wellbeing and which relate to different factors of personality. Below, we thus explore other (neutral) aspects of personality that potentially predict desire for privacy. In order to be more precise, we follow the advice by @Paunonen.2001 and, instead of using generic personality factors as predictors, refer to specific personality facets.

First, we argue that people who are more reserved, who feel less comfortable in social situations, generally desire more anonymity and more interpersonal privacy. Given that privacy is, by definition, a voluntary withdrawal from society [@Westin.1967], we expect that people who are more reserved or more shy desire more privacy from others. Several empirical studies support this hypothesis: Extroverted people desire less privacy [@Morton.2013], people who describe themselves as introverted thinkers are more likely to prefer social isolation [@Pedersen.1982], and introverted people are more likely to report invasions of privacy [@Stone.1986]. Finally, we did not find convincing theoretical and empirical arguments for why shyness should relate to an increased desire for privacy from government surveillance, which is why we did not include a hypothesis on this relation.

@@

### Anxiety

Of course, there are also reasons why people might desire less privacy. Government agencies often curtail privacy with the aim to prevent crime: For example, the NSA's surveillance programs are often considered a direct response to the 9 / 11 terrorists attacks [@Greenwald.2013]. It seems plausible that people who are more afraid of terrorist attacks are also more likely to consent to these surveillance programs, given that these programs promise to reduce the likelihood of future attacks. One can then argue that people who are afraid of terrorist attacks are also more afraid of threats overall, which is why we suggest that people who are, in general, more anxious desire less privacy from government surveillance and less anonymity. We did not include a hypothesis on the potential relation between anxiety and desire for interpersonal privacy. On the one hand, one could argue that people who are more anxious are more reserved, given that social interactions can pose significant risks [especially with strangers or weak ties; @Granovetter.1973]. At the same time, one could suggest that especially those people who are more anxious desire less privacy from others (and especially their strong ties), in order to cope better with their daily challenges. At the end, given that we measure interpersonal privacy on a general level (and do not distinguish between desire for privacy from (a) weak ties and (b) strong ties), it seems plausible that both effects could cancel each other out.

@@

### Risk aversion

Disclosing personal information always poses a certain risk, given that others can misuse self-disclosed personal information in different contexts, which can lead to severe consequences [@Altman.1976]. Not everyone will feel intimidated by this hypothetical threat---except those who have a general tendency to avoid taking unnecessary risks. The most cautious strategy to minimize risks of personal self-disclosures would be, arguably, to keep as much information as possible private. Hence, we suggest that people who are, in general, more risk averse have a good reason to desire more privacy in all three aforementioned contexts.

@@

### Traditionality

The personal computer and the Internet have rendered the world increasingly digitized: Social interactions, purchases, and medical treatments nowadays all produce digital traces, which can be combined into accurate latent user profiles. Given the features of digital information [i.e., information is persistent, searchable, reproducible, and scalable; @boyd.2008], this allows for unprecedented ways and degrees of surveillance. Mark Zuckerberg famously observed that privacy is no longer a "social norm," rather that people share personal information [@Johnson.2010]. Hence, in order to be part of contemporary life (e.g., by using SNSs), it seems necessary to give up some privacy. However, arguably not everyone is willing to pay that price, and especially people who are more conservative might prefer to stick to their usual routines and decide against giving up their privacy. This is supported by empirical research: Older people, who are generally less open and more traditional [@Donnellan.2008], are more concerned about their privacy than younger people [@Fife.2012]. Taken together, we suggest that people who are more traditional also desire more privacy in all three aforementioned contexts.

@@

# Methods

@@

## Procedure and participants

Participants were students from a university in the western U.S. who received course credit for taking part in the study. The sample consisted of _N_ = 296 respondents, with an age that ranged from 18 to 56 years (_M_ = 20 years). 72\% of the respondents were female. The median participation time was 24 minutes. Regarding ethnicity, 37\% of the respondents were Non-Hispanic White / Caucasian, 4\% Black / African American, 21\% Hispanic / Latino, 24\% Asian / Pacific Islander, 0\% Native American, 5\% others, and 8\% nonresponse.

## Measures

Despite the fact that we mostly used well-established scales, confirmatory factor analyses (CFAs) showed that some of the original items had to be deleted in order to achieve adequate factorial validity. The final scales showed acceptable fit (CFI \textgreater .90, TLI \textgreater .90, RMSEA \textless .10, SRMR \textless .10), good composite reliability (REL($\upomega$) \textgreater .60), and adequate convergent factorial validity (AVE \textgreater .50; see Table \ref{tab:DIS_Study_4_Table_1}). Respondents answered all items on a 7-point Likert scale ranging from 1 (_strongly disagree_) to 7 (_strongly agree_).

The data, all items (including deleted ones), results of CFAs, item statistics, and distribution plots can be found in the online supplementary material.[^OSM]

[^OSM]: https://osf.io/7ncpk/?view_only=38283fd9262646378e4ba1e19c9d707f}}

### Desire for privacy

We measured desire for privacy on three dimensions: (a) Desire for privacy from government surveillance, which represents the extent to which people want the government to abstain from collecting information about their personal life. One example item is "I feel the need to protect my privacy from government agencies." (b) Desire for anonymity, which measures the extent to which people feel the need to avoid identification("I need to be able to use a fake name on social network sites to preserve my privacy}). (c) Desire for privacy from other people, which measures the extent to which people want to withhold personal information from others("I don't feel the need to tell my friends all my secrets}). For each dimension, we used 3 self-developed items that build on prior studies [@Masur.2016].

### Integrity

>>>>

\documentclass[man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Who Needs Privacy?},
            pdfauthor={Tobias Dienlin~\& Miriam Metzger},
            pdfkeywords={keywords},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

  \title{Who Needs Privacy?}
    \author{Tobias Dienlin\textsuperscript{1}~\& Miriam Metzger\textsuperscript{1,2}}
    \date{}

\shorttitle{Who Needs Privacy?}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} University of Hohenheim\\\textsuperscript{2} University of California, Santa Barbara}
\keywords{keywords\newline\indent Word count: X}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

\usepackage{longtable}
\usepackage{lscape}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage[flushleft]{threeparttable}
\usepackage{threeparttablex}

\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

\linenumbers
\setlength{\parskip}{0em}
\raggedbottom

\authornote{Add complete departmental affiliations for each
author here. Each new line herein must be indented, like this line.

@@

Correspondence concerning this article should be addressed to Tobias
Dienlin, University of Hohenheim, Department of Media Psychology (540F).
E-mail:
\href{mailto:tobias.dienlin@uni-hohenheim.de}{\nolinkurl{tobias.dienlin@uni-hohenheim.de}}}

\abstract{
Objective: This study analyzes how personality relates to peoples'
desire for privacy. Specifically, we investigated whether the syllogism
``I don't mind surveillance because I have nothing to hide'' is correct:
Do people who lack integrity (given they have something to hide) indeed
desire more privacy?

Method: Study 1 featured an online questionnaire (\emph{N} = 268,
\emph{M}\textsubscript{age} = 20 years, 72\% female) and Study 2 a
laboratory experiment (\emph{N} = 87, \emph{M}\textsubscript{age} = 20
years, 51\% female), where participants wrote an essay about past
negative, positive, or neutral behaviors to analyze effects on desire
for privacy.

Results: Study 1 showed that respondents who are more shy, less anxious,
and more risk averse desired more privacy. Respondents who self-reported
lacking integrity reported desiring more privacy from government and
more anonymity. Study 2 replicated these results and showed a
statistical trend (\emph{p} = .052) that writing about negative past
behaviors increased desire for interpersonal privacy. Moreover, the
integrity IAT showed significant relations with desire for privacy from
government.

@@

}

\usepackage{amsthm}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\newtheorem{corollary}{Corollary}[section]
\newtheorem{proposition}{Proposition}[section]
\theoremstyle{definition}
\newtheorem{example}{Example}[section]
\theoremstyle{definition}
\newtheorem{exercise}{Exercise}[section]
\theoremstyle{remark}
\newtheorem*{remark}{Remark}
\newtheorem*{solution}{Solution}
\begin{document}
\maketitle

In his novel \emph{The Circle}, ({\textbf{???}}) describes a dystopian
society in which people are gradually forfeiting their privacy. People
decide to become \enquote{transparent}, which means that they start
carrying a small camera around the neck in order to broadcast their
daily lives to the Internet. Eventually, this causes a societal
upheaval: \enquote{The pressure on those who hadn't gone transparent
went from polite to oppressive. The question, from pundits and
constituents, was obvious and loud: If you aren't transparent, what are
you hiding?} ({\textbf{???}}). The main argument being offered to
justify the surveillance is: \enquote{If you have nothing to hide, you
have nothing to fear.} This syllogism is familiar, given that it
commonly appears in also nonfictional conversations ({\textbf{???}}).
Consider, for example, the following tweet: \enquote{I don't download
illegally. I don't have anything on my comp{[}uter{]} to hide. Hell, I'm
sure the \#NSA gave up on me years ago.} ({\textbf{???}}).

Why do people desire privacy? To date there is only little research on
why people desire privacy and how the desire for privacy can be
predicted by aspects of personality. For example, and to the best of our
knowledge, so far no study exists that has analyzed the nothing-to-hide
argument from a scientific and empirical perspective. Why do some people
not care whether government agencies such as the NSA are collecting
their data ({\textbf{???}}), and why do others protest vehemently in
order to protect their privacy?

@@

\hypertarget{desire-for-privacy}{%
\subsection{Desire for Privacy}\label{desire-for-privacy}}

Privacy captures the extent of voluntary withdrawal from others (Westin,
1967). Several models suggest that privacy is a multi-dimensional
concept: For example, in a theory-driven treatise ({\textbf{???}})
argued that privacy has four dimensions: informational, social,
psychological, and physical privacy. Pedersen (1979), by contrast, did
an empirical factor analysis (initially starting with 94 items) and
suggested that privacy exists on six dimensions: reserve, isolation,
solitude, intimacy with friends, intimacy with family, and anonymity. In
addition, Schwartz (1968) differentiated between horizontal and vertical
privacy: Whereas horizontal privacy captures withdrawal from peers,
vertical privacy refers to withdrawal from superiors or institutions
(e.g., government agencies). Next to being multi-dimensional, privacy is
also contingent (Dienlin, 2014): One can, for example, distinguish
between the objective privacy context, the subsequent subjective
perception of privacy, the psychological desire for privacy (which is
both a situational and dispositional need), and the resulting privacy
behavior (as represented by self-disclosure). For the purpose of this
study, we combine the aforementioned theories and focus on (a) vertical
privacy with regard to the desire for withdrawal from government
surveillance, (b) horizontal privacy in terms of the desire for
withdrawal from peers, friends, or acquaintances, and (c) both
horizontal and vertical privacy as captured by the general desire for
anonymity.

\hypertarget{the-relation-between-integrity-and-desire-for-privacy}{%
\subsubsection{The relation between integrity and desire for
privacy}\label{the-relation-between-integrity-and-desire-for-privacy}}

@@

The NSA surveillance, data mining, or other government information
gathering programs will result in the disclosure of particular pieces of
information to a few government officials, or perhaps only to government
computers. This very limited disclosure of the particular information
involved is not likely to be threatening to the privacy of law-abiding
citizens. Only those who are engaged in illegal activities have a reason
to hide this information. {[}({\textbf{???}}); p.~753{]}

This definition helps illustrate the link between lack of integrity and
desire for privacy: People who have \enquote{engaged in illegal
activities} can be considered, by definition, to lack integrity
({\textbf{???}}), which is why they have a reason \enquote{to hide this
information} (or, in other words, to desire more privacy). In terms of a
scientific definition of integrity there is no real consensus, however
most scholars agree that integrity \enquote{incorporates a tendency to
comply with social norms, avoid deviant behavior, and embrace a sense of
justice, truthfulness, and fairness} {[}({\textbf{???}}); p.~82{]}.

Several theoretical arguments exist why lack of integrity might
correlate with desire for privacy. In general, any self-disclosure is a
potential risk because others might disagree, disapprove, or misuse the
information in other contexts ({\textbf{???}}). Privacy regulation
theory showed that if self-disclosures are too risky, people raise their
desired level of privacy, intensify their boundary regulation, and
employ more mechanisms to seclude and protect themselves
({\textbf{???}}). In traditional contexts, this could range from
moderate behaviors like closing doors, to extreme behaviors such as
physically tossing someone out of the room ({\textbf{???}}). In modern
contexts, protecting one's privacy can mean to avoid photographs or to
deliberately shun public places that have surveillance cameras. People
who have actually committed something bad, treacherous, or illegal
become even more vulnerable and face a significant risk of
self-disclosure, because others will surely disapprove of these
activities ({\textbf{???}}). Hence, the foregoing arguments illuminate
an indirect link between integrity and desire for privacy: By
definition, people who participate in negative activities are considered
to lack integrity ({\textbf{???}}). People who have engaged in negative
activities have, by definition, more to hide, and disclosures concerning
those activities pose a high risk. Because of this increased risk,
people will arguably desire more privacy, as a means to mitigate their
felt risk ({\textbf{???}}). In this way, the current research extends
Altman's privacy regulation theory (1976) by suggesting that lack of
integrity is an important yet unexamined factor that could increase
peoples' desired level of privacy.

A few studies can be found that imply a relation between privacy and
integrity. For example, several studies found that surveillance reduces
cheating behaviors ({\textbf{???}}, Covey.1989). ({\textbf{???}}) asked
students to solve an impossible maze. In the high surveillance
condition, the experimenter stood in front of the students and closely
monitored their behavior. In the low surveillance condition, the
experimenter stood behind the students, did not monitor their behavior,
and visual dividers were used to block the experimenter's view of the
students. Results showed that students were more likely to cheat in the
low surveillance condition, suggesting that in situations of
surveillance (i.e., less privacy), people show fewer cheating behaviors
(i.e., more integrity). Similarly, people are more likely to prevent
others from stealing when security cameras are visible ({\textbf{???}}),
which is also a sign of higher integrity. Next, in a longitudinal sample
with 457 respondents in Germany ({\textbf{???}}), people who reported
needing more privacy were less satisfied with their lives (\emph{r} =
-.47), had more (\emph{r} = .41) and less positive affect (\emph{r} =
-.39). More importantly however, people who felt they needed more
privacy were also less authentic on their SNSs profiles (\emph{r} =
-.48) and less authentic in their personal relationships (\emph{r} =
-.28; {\textbf{???}}). For example, people who agreed to items like
\enquote{I do not talk about personal issues unless my conversation
partner brings them up first} were more likely to report that their
online profiles did not truly represent their personality. Given the
argument that authenticity is a subset of integrity ({\textbf{???}}), we
reason that the concept of integrity might relate to the desired level
of privacy. Finally, Pedersen (1982) showed that three dimensions of
need for privacy related to self-esteem: In his study with \emph{N} = 70
undergraduate students, respondents who held a lower self-esteem were
more reserved (\emph{r} = .29), needed more anonymity (\emph{r} = .21)
and preferred solitude (\emph{r} = .24). Granted, self-esteem and
integrity are generally distinct concepts; however, Pedersen's specific
operationalization of self-esteem integrated several aspects of
integrity (e.g., by using items such as \enquote{moral, nice, fair,
unselfish, good, honest, reputable, sane} to measure self-esteem). Thus,
our overarching hypothesis is that people who lack integrity have a
greater desire for privacy.

@@

\hypertarget{shyness}{%
\subsubsection{Shyness}\label{shyness}}

Critics of the nothing-to-hide argument hold that people who desire
privacy should not automatically be confronted with suspicion, and that
privacy has several purposes that are not related to criminal behavior
({\textbf{???}}). Westin (1967), for example, defined four primary
purposes of privacy: (1) self-development (i.e., the integration of
experiences into meaningful patterns), (2) autonomy (i.e., the desire to
avoid being manipulated and dominated), (3) emotional release (i.e., the
release of tension from social role demands), and (4) protected
communication (i.e., the ability to foster intimate relationships).
These are all important social factors for which people desire privacy.
Hence, the argument is that people who desire privacy can have several
legitimate reasons for doing so; reasons which are essential for
psychosocial wellbeing and which relate to different factors of
personality. Below, we thus explore other (neutral) aspects of
personality that potentially predict desire for privacy. In order to be
more precise, we follow the advice by Paunonen and Ashton (2001) and,
instead of using generic personality factors as predictors, refer to
specific personality facets.

First, we argue that people who are more reserved, who feel less
comfortable in social situations, generally desire more anonymity and
more interpersonal privacy. Given that privacy is, by definition, a
voluntary withdrawal from society (Westin, 1967), we expect that people
who are more reserved or more shy desire more privacy from others.
Several empirical studies support this hypothesis: Extroverted people
desire less privacy ({\textbf{???}}), people who describe themselves as
introverted thinkers are more likely to prefer social isolation
(Pedersen, 1982), and introverted people are more likely to report
invasions of privacy ({\textbf{???}}). Finally, we did not find
convincing theoretical and empirical arguments for why shyness should
relate to an increased desire for privacy from government surveillance,
which is why we did not include a hypothesis on this relation.

@@

\hypertarget{anxiety}{%
\subsubsection{Anxiety}\label{anxiety}}

Of course, there are also reasons why people might desire less privacy.
Government agencies often curtail privacy with the aim to prevent crime:
For example, the NSA's surveillance programs are often considered a
direct response to the 9 / 11 terrorists attacks ({\textbf{???}}). It
seems plausible that people who are more afraid of terrorist attacks are
also more likely to consent to these surveillance programs, given that
these programs promise to reduce the likelihood of future attacks. One
can then argue that people who are afraid of terrorist attacks are also
more afraid of threats overall, which is why we suggest that people who
are, in general, more anxious desire less privacy from government
surveillance and less anonymity. We did not include a hypothesis on the
potential relation between anxiety and desire for interpersonal privacy.
On the one hand, one could argue that people who are more anxious are
more reserved, given that social interactions can pose significant risks
(especially with strangers or weak ties; {\textbf{???}}). At the same
time, one could suggest that especially those people who are more
anxious desire less privacy from others (and especially their strong
ties), in order to cope better with their daily challenges. At the end,
given that we measure interpersonal privacy on a general level (and do
not distinguish between desire for privacy from (a) weak ties and (b)
strong ties), it seems plausible that both effects could cancel each
other out.

@@

\hypertarget{risk-aversion}{%
\subsubsection{Risk aversion}\label{risk-aversion}}

Disclosing personal information always poses a certain risk, given that
others can misuse self-disclosed personal information in different
contexts, which can lead to severe consequences ({\textbf{???}}). Not
everyone will feel intimidated by this hypothetical threat---except
those who have a general tendency to avoid taking unnecessary risks. The
most cautious strategy to minimize risks of personal self-disclosures
would be, arguably, to keep as much information as possible private.
Hence, we suggest that people who are, in general, more risk averse have
a good reason to desire more privacy in all three aforementioned
contexts.

@@

\hypertarget{traditionality}{%
\subsubsection{Traditionality}\label{traditionality}}

The personal computer and the Internet have rendered the world
increasingly digitized: Social interactions, purchases, and medical
treatments nowadays all produce digital traces, which can be combined
into accurate latent user profiles. Given the features of digital
information (i.e., information is persistent, searchable, reproducible,
and scalable; {\textbf{???}}), this allows for unprecedented ways and
degrees of surveillance. Mark Zuckerberg famously observed that privacy
is no longer a \enquote{social norm,} rather that people share personal
information ({\textbf{???}}). Hence, in order to be part of contemporary
life (e.g., by using SNSs), it seems necessary to give up some privacy.
However, arguably not everyone is willing to pay that price, and
especially people who are more conservative might prefer to stick to
their usual routines and decide against giving up their privacy. This is
supported by empirical research: Older people, who are generally less
open and more traditional ({\textbf{???}}), are more concerned about
their privacy than younger people ({\textbf{???}}). Taken together, we
suggest that people who are more traditional also desire more privacy in
all three aforementioned contexts.

@@

\hypertarget{methods}{%
\section{Methods}\label{methods}}

@@

\hypertarget{procedure-and-participants}{%
\subsection{Procedure and
participants}\label{procedure-and-participants}}

Participants were students from a university in the western U.S. who
received course credit for taking part in the study. The sample
consisted of \emph{N} = 296 respondents, with an age that ranged from 18
to 56 years (\emph{M} = 20 years). 72\% of the respondents were female.
The median participation time was 24 minutes. Regarding ethnicity, 37\%
of the respondents were Non-Hispanic White / Caucasian, 4\% Black /
African American, 21\% Hispanic / Latino, 24\% Asian / Pacific Islander,
0\% Native American, 5\% others, and 8\% nonresponse.

\hypertarget{measures}{%
\subsection{Measures}\label{measures}}

Despite the fact that we mostly used well-established scales,
confirmatory factor analyses (CFAs) showed that some of the original
items had to be deleted in order to achieve adequate factorial validity.
The final scales showed acceptable fit (CFI \textgreater .90, TLI
\textgreater .90, RMSEA \textless .10, SRMR \textless .10), good
composite reliability (REL(\(\upomega\)) \textgreater .60), and adequate
convergent factorial validity (AVE \textgreater .50; see Table
\ref{tab:DIS_Study_4_Table_1}). Respondents answered all items on a
7-point Likert scale ranging from 1 (\emph{strongly disagree}) to 7
(\emph{strongly agree}).

The data, all items (including deleted ones), results of CFAs, item
statistics, and distribution plots can be found in the online
supplementary material.\footnote{\url{https://osf.io/7ncpk/?view_only=38283fd9262646378e4ba1e19c9d707f}\}\}}

\hypertarget{desire-for-privacy-1}{%
\subsubsection{Desire for privacy}\label{desire-for-privacy-1}}

We measured desire for privacy on three dimensions: (a) Desire for
privacy from government surveillance, which represents the extent to
which people want the government to abstain from collecting information
about their personal life. One example item is \enquote{I feel the need
to protect my privacy from government agencies.} (b) Desire for
anonymity, which measures the extent to which people feel the need to
avoid identification(\enquote{I need to be able to use a fake name on
social network sites to preserve my privacy\}). (c) Desire for privacy
from other people, which measures the extent to which people want to
withhold personal information from others(}I don't feel the need to tell
my friends all my secrets\}). For each dimension, we used 3
self-developed items that build on prior studies ({\textbf{???}}).

\hypertarget{integrity}{%
\subsubsection{Integrity}\label{integrity}}

Integrity measures the extent to which people comply with social norms
and values. When measuring integrity, the question arises whether it is
possible to measure integrity based on self-reports. Interestingly,
integrity tests that are based on self-reports have been shown to work
successfully, given that they can predict unwanted professional
workplace behavior sufficiently (e.g., theft, drug and alcohol problems,
or absenteeism; {\textbf{???}}). In order to measure lack of integrity,
we thus used 4 items of the subscale integrity of the Supernumerary
Personality Inventory ({\textbf{???}}). An example item is \enquote{I
don't think there's anything wrong with cheating a little on one's
income tax forms.}
